Reducing RES Droughts through the integration of wind and PV

### 2025-01-16 Article/RES_droughts_Morin_ReEn.tex
New Article Template for Renewable Energy

@@

The EU aims to generate at least 69\% of its electricity from renewable energy sources (RES) by 2030, up from 41\% in 2022 \citep{eurostat2023share}. While this transition is essential for reducing greenhouse gas emissions, it also highlights the challenge of managing the variability of weather-dependent energy sources such as wind and photovoltaic (PV) power. This challenge is compounded by the increasing electrification of energy sectors, which places greater demand on the power system and makes it more sensitive to meteorological conditions~\citep{bloomfield2016, bloomfield2021, vanderWiel2019drought}. Periods of low renewable generation, known as \textit{Dunkelflaute} or RES droughts, pose significant risks to system adequacy and energy security, emphasizing the need for a resilient energy system to meet both growing electricity demand and decarbonization targets.

@@

%% If you have bib database file and want bibtex to generate the
%% bibitems, please use

\bibliographystyle{elsarticle-harv}
\bibliography{litrev}

>>>>

%% Use this package to add line brakes in URL
\usepackage{xurl}

@@

The EU aims to generate at least 69\% of its electricity from renewable energy sources (RES) by 2030, up from 41\% in 2022 \citep{eurostat2023share}. While this transition is essential for reducing greenhouse gas emissions, it also highlights the challenge of managing the variability of weather-dependent energy sources such as wind and photovoltaic (PV) power. This challenge is compounded by the increasing electrification of energy sectors, which places greater demand on the power system and makes it more sensitive to meteorological conditions~\citep{bloomfield2016, bloomfield2021, vanderwiel2019drought}. Periods of low renewable generation, known as \textit{Dunkelflaute} or RES droughts, pose significant risks to system adequacy and energy security, emphasizing the need for a resilient energy system to meet both growing electricity demand and decarbonization targets.

@@

\section*{Data Availability}

The meteorological data, including wind speed, irradiance, and temperature, can be accessed through the Climate Data Store (\url{https://doi.org/10.24381/cds.adbb2d47}). The C3S-E dataset is also available from the Climate Data Store (\url{https://doi.org/10.24381/cds.4bd77450}). Information on wind and PV farms in Ireland can be obtained from the EirGrid website (\url{https://www.eirgrid.ie/grid/system-and-renewable-data-reports}). The Atlite scripts used in this study are open-source and can be found on GitHub (\url{https://github.com/pypsa/atlite}). The data required to reproduce the figures in this article will be made available upon acceptance of the manuscript.

\bibliographystyle{elsarticle-harv}
\bibliography{RES_droughts_Morin_ref}
